---
title: "NMDC_Test"
author: "npc"
date: "`r Sys.Date()`"
output:
  github_document: default
  html_document: default
knit: (function(inputFile, encoding) {
                rmarkdown::render(inputFile,
                                  encoding = encoding,
                                  output_format = "all") 
        })
---

# README

This repo contains answers to pre-interview questions assigned before an interview for an NMDC position.

```{r, include = TRUE, echo = TRUE}
# load in some libraries and set the WD
suppressMessages(library(utils))
suppressMessages(library(yaml))
suppressMessages(library(jsonlite))
suppressMessages(library(httr))
setwd("~/Repos/NMDC_Test")
source(file = "R/Biosample_Metadata.R")
```

## Question 1:
*Write a script to download the metadata from one NMDC’s biosample API endpoints for biosample id nmdc:bsm-11-q84vp418 and return the values for id, habitat, and gold_biosample_identifiers.*

A brief barebones function can be constructed in R that semi-flexibly pulls data from the NMDC API endpoints. This function only relies on two packages that are not in base R, `httr` and `jsonlite`. The function is present in the `R` directory, while a script that loads the function and attempts to print out the requested metadata in relatively acceptable formating is present in the `Scripts` directory. A brief example of the function in use is provided in the code chunk below.

```{r, include = TRUE, echo = TRUE}
res1 <- Biosample_Metadata(metadata1 = "id",
                           annotations = "habitat",
                           alternative_IDs = "GOLD",
                           ID = "nmdc:bsm-11-q84vp418")
print(res1)
```

## Question 2:
*Review the existing docker containers available on dockerhub for SPAdes, a common assembler for metagenomic datasets, and describe how you would determine which, if any, of the existing containers you would use versus writing one from scratch.*

SPAdes has included it's `--meta` mode for a while, so any container that is successfully installing a recent version of SPAdes should be acceptable for assembly alone. Pre- and post-assembly tasks like binning and quality control would require other tools though. How that work is divided up is largely a choice dependent upon available resources, and tool dependencies. A dockerfile that constructs a custom container with common tools for read QC, assembly, and binning is present in the `Container01` directory of this repo.

## Question 3:
*Using a workflow management tool of your choice, write a portable workflow which 1) runs the SPAdes test dataset (spades.py --test) and 2) returns the version of SPAdes used.*

A workflow for testing SPAdes using CWL is constructed below. A dockerfile that constructs the container these were tested in is present in the `Container01` directory of this repo, and the generated `.cwl` files are deposited in the `Scripts` folder of this repo. In brief, two cwl processes are invoked by a single cwl workflow to run and capture the stdout for `spades.py --test` and `spades.py --version`. This container can also be pulled locally for testing with `docker pull npcooley/nmdctest01:1.0`. With all three `.cwl` files in the home directory and `spades.py` present in the `$PATH` variable, `cwltool combine.cwl` should run to completion and return two text files, `res1.txt` containing the stdout from running the spades test set, and `res2.txt` containing the version info for the spades installation.

```{r, include = TRUE, echo = TRUE}

suppressMessages(library(yaml))

TEST <- as.yaml(list("cwlVersion" = "v1.0",
                     "class" = "CommandLineTool",
                     "baseCommand" = c("spades.py", "--test"),
                     "stdout" = "res1.txt",
                     "inputs" = list(),
                     "outputs" = list("example_out" = list("type" = "stdout"))))
TEST <- gsub(pattern = "'",
             replacement = "",
             x = TEST)
# cat(TEST)

VER <- as.yaml(list("cwlVersion" = "v1.0",
                    "class" = "CommandLineTool",
                    "baseCommand" = c("spades.py", "--version"),
                    "stdout" = "res2.txt",
                    "inputs" = list(),
                    "outputs" = list("example_out" = list("type" = "stdout"))))
VER <- gsub(pattern = "'",
            replacement = "",
            x = VER)
# cat(VER)

COMBINE <- as.yaml(list("cwlVersion" = "v1.0",
                        "class" = "Workflow",
                        "inputs" = list(),
                        "outputs" = list("out" = list("type" = "File",
                                                      "outputSource" = "step1/example_out"),
                                         "res" = list("type" = "File",
                                                      "outputSource" = "step2/example_out")),
                        "steps" = list("step1" = list("run" = "test.cwl",
                                                      "in" = list(),
                                                      "out" = "[example_out]"),
                                       "step2" = list("run" = "version.cwl",
                                                      "in" = list(),
                                                      "out" = "[example_out]"))))
COMBINE <- gsub(pattern = "'",
                replacement = "",
                x = COMBINE)
# cat(COMBINE)

writeLines(TEST, "Scripts/test.cwl")
writeLines(VER, "Scripts/version.cwl")
writeLines(COMBINE, "Scripts/combine.cwl")

```

## Question 4:
*Clone the nmdc-schema repository or use the UI documentation to list the required slots for Class OmicsProcessing.*

A brief R workflow for scraping the required slots for the `OmicsProcessing` class is included in the R code chunk below:

```{r, include = TRUE, echo = TRUE}

suppressMessages(library(rvest))

# scrape the page
res2 <- read_html("https://microbiomedata.github.io/nmdc-schema/OmicsProcessing/")
# grab the tables
res3 <- html_table(res2)
# slots are the first table, print the first column:
print(res3[[1]]$Name)

# find out the required slots:
temp1 <- tempfile()
res3 <- html_text(html_elements(res2, "#induced+ details"))
writeLines(res3, temp1)
res4 <- read_yaml(temp1)

# there are no 'required: FALSE' slots in the YAML, so can just look for 'required' as the list name
res5 <- res4$slot_usage
req_by_slot <- sapply(X = res5,
                      FUN = function(x) {
                        "required" %in% names(x)
                      })
req_by_slot <- names(req_by_slot)[req_by_slot]
# print out slots that have a required slot
print(req_by_slot)
res6 <- res4$attributes
req_by_attribute <- sapply(X = res6,
                           FUN = function(x) {
                             "required" %in% names(x)
                           })
req_by_attribute <- names(req_by_attribute)[req_by_attribute]
# print out slots that have a required slot
print(req_by_attribute)
```

## session stuff

```{r, include = TRUE, echo = FALSE}
# session info
sessionInfo()
# r version
version
```

